What can we learn about life in the city by mining the Melbourne’s Open Data Platform?

### 2017-05-06 thesis/proposal_draft.Rmd
update- close to final

\begin{center}
\textbf{Figure 3}: Pedestrian Counting System Visualisation from www.pedestrian.melbourne.vic.gov.au - The UI allows the user to choose specific dates and hours of the day to visualise on a 3D perspective map

@@

#### Visualisation  
Ideally, having a dynamic spatial model would allow us to visualise the pedestrian activity in areas not covered by the currently installed sensors. However, due to time constraints, the visualisation will most likely be based on a model of predictions of pedestrian counts at each sensor location.

>>>>

\begin{center}
\textbf{Figure 3}: Pedestrian Counting System Visualisation from www.pedestrian.melbourne.vic.gov.au - The UI allows the user to choose specific dates and hours of the day to visualise on a 3D perspective map. The visualisation can also animate pedestrian activity, allowing for changes over time to be easily seen.

@@

#### Visualisation  
Ideally, having a dynamic spatial model would allow us to visualise the pedestrian activity in areas not covered by the currently installed sensors. However, due to time constraints, the visualisation will most likely be based on a model of predictions of pedestrian counts at each sensor location. Improvements to the quality of the map can be made with utilisation of the R package `leaflet`. Other packages being explored for visualisations also include `plotly`.
